Sampling Strategies in Decisions from Experience

### 2021-12-10 manuscript.Rmd
Change thesis title

---
title             : "Sampling Strategies in Decisions from Experience"
shorttitle        : "Sampling in Decisions from Experience"

>>>>

---
title             : "Sampling Strategies in Decisions from Experience: Property Representation and Probability Weighting Approximation"
shorttitle        : "Sampling strategies in decisions from experience"
